Pragmatics account for apparent limits on theory of mind use in adults

### 2016-01-24 writing/cogsci-submission/cogsci_keysar.tex
comments on exp2 analysis

@@

Next, we test whether these reductions in error rate and hover-time interference are in fact due to different speaker behavior. Two coders were given the list of messages that directors sent to convey instructions for critical items, blind to condition. The coders determined (1) whether or not the label used by the speaker fit the hidden distractor and (2) whether or not the label used by the director was more or less precise than the scripted label used in Exp.~1. Inter-rater reliability was relatively high, with $r=0.82$ for distractor fit and $r=0.69$ for the precision comparison. Binary rater decisions were averaged to form a single distractor fit score for each message, and a single precision score.

We found that the referring expressions speakers used to convey critical instructions only fit the distractor 53\% of the time, compared to the scripted message in Exp.~1, which fit the distractor 100\% of the time. Furthermore, 47\% of these referring expressions were rated to be more precise than the corresponding scripted instruction used in Exp.\~1. As expected, there's a strong negative relationship between the precision of the label and whether it might apply to the hidden distractor, $r = -0.73$. Finally, we test whether the speaker's choice of label accounts for variability in error rates across different items. We find that error rates are higher when the speaker's label fits the hidden distractor $b = 0.79, t(5) = 2.8, p = 0.36$ \todo[inline]{rdh: this isn't the right regression... I did it on the aggregated scores, and it should really be done on the raw subject-by-subject data. It's just a bit tricky to join the error data and the message data.}

\begin{figure}[b!]
\begin{center}
\includegraphics[scale=.75]{images/exp2MouseTracking.pdf}
\caption{Mean percentage of time spent hovering over the distractor and target cells in the experimental and baseline conditions. Error bars are 95\% confidence intervals.}
\label{fig:exp2hover}
\end{center}
\end{figure}
\section{Exp.~2: Unscripted Replication}
\label{sec:Exp2}

>>>>

\section{Exp.~2: Unscripted Replication}
\label{sec:Exp2}

@@

Next, we test whether these reductions in error rate and hover-time interference are in fact due to different speaker behavior. Two coders were given the list of messages that directors sent to convey instructions for critical items, blind to condition. The coders determined (1) whether or not the label used by the speaker fit the hidden distractor and (2) whether or not the label used by the director was more or less precise than the scripted label used in Exp.~1. Inter-rater reliability was relatively high, with $r=0.82$ for distractor fit and $r=0.69$ for the precision comparison. \ndg{r is not right measure of agreement for binary coding -- \%agreement or kappa?} Binary rater decisions were averaged to form a single distractor fit score for each message, and a single precision score.

We found that the referring expressions speakers used to convey critical instructions only fit the distractor 53\% of the time, compared to the scripted message in Exp.~1, which fit the distractor 100\% of the time. Furthermore, 47\% of these referring expressions were rated to be more precise than the corresponding scripted instruction used in Exp.~1. \ndg{was remaining 53\% rated as scripted more precise or mostly `can't tell'?} As expected, there's a strong negative relationship between the precision of the label and whether it might apply to the hidden distractor, $r = -0.73$. Finally, we test whether the speaker's choice of label accounts for variability in error rates across different items. We find that error rates are higher when the speaker's label fits the hidden distractor $b = 0.79, t(5) = 2.8, p = 0.36$ \todo[inline]{rdh: this isn't the right regression... I did it on the aggregated scores, and it should really be done on the raw subject-by-subject data. It's just a bit tricky to join the error data and the message data.}
\ndg{also it's not clear what that analysis is, or how it tells us about the item effects...}

\begin{figure}[b!]
\begin{center}
\includegraphics[scale=.75]{images/exp2MouseTracking.pdf}
\caption{Mean percentage of time spent hovering over the distractor and target cells in the experimental and baseline conditions. Error bars are 95\% confidence intervals.}
\label{fig:exp2hover}
\end{center}
\end{figure}
